Building a Probabilistic Model with Deep Neural Networks for Camera Geo-Calibration

### 2018-06-26 chapters/introduction/introduction.tex
minor change

The ultimate goal of image understanding is to transfer the visual
images into numerical or symbolic descriptions of the world
that are helpful for other thought processes for decision making.
In general, understanding images is not trivial for machines.
For different application scenarios, researchers divide image
understanding into different computer vision tasks. For example,
pedestrian detection is essential to autonomous driving, and image
retrieval to an image searching engine.

>>>>

The ultimate goal of image understanding is to transfer the visual
images into numerical or symbolic descriptions of the world
that are helpful for other thought processes for decision making.
In general, understanding images is not trivial for machines.
Under different scenarios, researchers divide image
understanding into different computer vision tasks. For example,
pedestrian detection is essential to autonomous driving, and image
retrieval to an image searching engine.

As one of the primary vision tasks, camera calibration plays an
important role in many applications like indoor layout estimation and
image mensuration. 
In the camera pin-hole model, camera calibration parameters consist of
the camera intrinsics and the extrinsic. The intrinsic parameters of
a camera encode information of the camera itself such as focal length,
principal point \etc; the extrinsic parameters are referred to as the
external states of the camera, such as the camera poses and
offset/location under some coordinate system. Specifically,
camera geo-calibration consider the camera locations in the geographic
coordinates.
In this work, our study mainly focus on the extrinsic like camera pose
and the geo-orientation/geo-localization of the camera.

In current work of camera calibration, most algorithms are
deterministic, which means they output fixed solutions. Applications
that takes probabilistic inputs (especially for those which use
graphic model) don't like it. To address this, we propose to build a
probabilistic model for camera geo-calibration.

### 2018-06-26 dissertation.tex
minor change

\abstract
{ \SingleSpacing
Camera calibration is one of the primary task in computer vision.
It plays an important role in applications like SLAM, image
mensuration and indoor layout estimation. Current models for camera
calibration are mostly deterministic, namely they output fixed
solutions. However, applications built with graphic models favor
probabilistic inputs, of which these deterministic calibration
models are not capable.
To address this problem, we propose a probabilistic model with deep
neural networks (DNNs) for camera
geo-calibration, providing more flexible inputs for applications that
are interfaced camera calibration parameters. Compared to 
traditional camera calibration, camera geo-calibration measures the
camera extrinsic in geographic coordinates.
Furthermore, our approaches also demonstrate that the geographic
information is helpful for extracting/transferring high level
features in DNN training.
The primary contributions of our thesis include building a
probabilistic model fro camera geo-calibration ,and relating the
camera geographic information and image semantics through deep neural
networks. Our discoveries can provide researchers new insights for
both camera calibration and DNN training.
}
\keywords{geo-calibration, deep neural networks, computer vision}

>>>>

\abstract
{ \SingleSpacing
Camera calibration is one of the primary task in computer vision.
It plays an important role in applications like SLAM, image
mensuration and indoor layout estimation. Current models for camera
calibration are mostly deterministic, namely they output fixed
solutions. However, applications built with graphic models favor
probabilistic inputs, of which these deterministic calibration
models are not capable.
To address this problem, we propose a probabilistic model with deep
neural networks (DNNs) for camera
geo-calibration, providing more flexible inputs for applications that
are interfaced camera calibration parameters. Compared to 
traditional camera calibration, camera geo-calibration measures the
camera extrinsic in geographic coordinates.
Furthermore, our approaches also demonstrate that the geographic
information is helpful for extracting/transferring high level
features in DNN training.
The primary contributions of our thesis include building a
probabilistic model for camera geo-calibration ,and relating the
camera geographic information and image semantics through deep neural
networks. Our discoveries can provide researchers new insights for
both camera calibration and DNN training.
}
\keywords{geo-calibration, deep neural networks, computer vision}
